My title

### 2024-09-14 outputs/paper/paper.qmd
First edit of discussion

# Discussion

>>>>

# Discussion
Based on the analysis of results section, we observe that, even though the overall population of homeless people did not incur sgnificant variation in the past six years, its demographics changed a lot. Especially, the proportion of refugees, chronic people as well as working aged people. In the past, City of Toronto has devolted its effort on reducing the number of homeless people, espically through projects of building affordable houses @torontosol. However, our study show that with the change of demographic, the city government should also give its focus on other strategies of reducing homelessness.

First, as the result section points out, the proportion of chronically homeless people nearly doubled in the past six years. Despite its nature of long-lasting homeless status, studies have also shown that chronic homelessness is closely associated with chronic illness or mental problems @chronic. As pointed out by another study, the average income of people experiencing mental illness and other types of disorders is significantly lower than that of normal people @Sareen2011. Thus, it is very hard for those people who have already experienced mental and physical illness to escape homelessness. In addition, homeless people would face more severe health problems due to lack of adequate food, discrimination, barriers to health care, etc @Sleet2021. A combination of these would become an obvious negative cycle: illness leads to a decrease in income, which leads to becoming homeless, which would further depend on illness. What the city government can do, on the other hand, is to increase the public health care system, especially focused on low-income and homeless people. In fact, merely building houses only increased the proportion of chronically homeless people and its aim is to reduce @house_not.

Second, due to increased global conflict in Eastern Europe and the Middle East, the number of refugees entering Toronto has increased @cbc23.On the other hand, the Toronto government has not been prepared to support such a huge increase of refugees as the portion of refugees in homeless people roared from less than 20% in the first three quarters of 2021 to nearly 60% at second quarter 2024. We observe an emergency for the government to increase its speed of helping these newly entered refugees and give them a job and a secure place to live.

Finally, we observe an increase in the proportion of people of worked-age. This indicates the need of the government to create more jobs for the people who need it to make a living, like people who are experiencing mental health problems or physical disabilities.
